Fast Algorithms for Intersection of Non-matching Grids Using \plucker Coordinates.

### 2016-11-26 paper_intersections.tex
Improve notation and explanation of plucker coordinates.

%commands:
%\newcommand{\defref}[1]{\hyperref[#1]{Def.~\ref{#1}}}
\newcommand{\prob}[1]{Problem~{#1}}
\newcommand{\fig}[1]{\hyperref[#1]{Figure \ref{#1}}}
\newcommand{\figpath}{}

@@

\subsection{\plucker Coordinates}
\plucker coordinates represent a line in 3d space.
Considering a line $p$, given by a point $\vc A$ and its directional vector $\vc{u}$, 
the \plucker coordinates of $p$ are defined as
\[ \pi_p = (\vc{u}_p, \vc{v}_p) = (\vc{u}_p, \vc{u}_p\times \vc A). \]
Further we denote a permuted inner product
\[\pi_p \odot \pi_q = \vc{u}_p\cdot \vc{v}_q + \vc{u}_q \cdot \vc{v}_p. \]

The sign of the permuted inner product gives us the relative position of the two lines, 
see \fig{fig:plucker_products}.

\begin{figure}[!htb]
    \centering    
    \subfloat[$\pi_p\odot \pi_i < 0 \;\forall i$]{
        \includegraphics[width=0.3\textwidth]{\figpath plucker_product_a.pdf}
    }
    \subfloat[$\pi_p\odot \pi_i = 0 \, \exists i$ \newline special case]{
        \includegraphics[width=0.3\textwidth]{\figpath plucker_product_b.pdf}
    }
    \subfloat[$\pi_p\odot \pi_i > 0 \;\forall i$]{
        \includegraphics[width=0.3\textwidth]{\figpath plucker_product_c.pdf}
    }
    \caption{Sign of the permuted inner product is related to the relative position of the two oriented lines.          
            Dashed line symbolizes that the line is in the back, the lines intersect in the middle case.
    }
    \label{fig:plucker_products}
\end{figure}

>>>>

%commands:
%\newcommand{\defref}[1]{\hyperref[#1]{Def.~\ref{#1}}}
\newcommand{\prob}[1]{Problem~{#1}}
\newcommand{\fig}[1]{\hyperref[#1]{Figure \ref{#1}}}
% \newcommand{\figpath}{}
\newcommand{\figpath}{figures/}

@@

\subsection{\plucker Coordinates}
\plucker coordinates represent a line in 3d space.
Considering a line $p$, given by a point $\vc A$ and its directional vector $\vc{u}_p$, 
the \plucker coordinates of $p$ are defined as
\[ \pi_p = (\vc{u}_p, \vc{v}_p),\; \vc{v}_p = \vc{u}_p\times \vc A. \]
Further, having two lines $p$ and $q$ with \plucker coordinates $\pi_p$ and $\pi_q$, we denote a permuted inner product
\[\pi_p \odot \pi_q = \vc{u}_p\cdot \vc{v}_q + \vc{u}_q \cdot \vc{v}_p. \]

The sign of the permuted inner product tells us the relative position of two lines, 
which is demonstrated on an example of a relative position of a line and a triangle sides in \fig{fig:plucker_products}.

\begin{figure}[!htb]
    \centering
    \subfloat[$\pi_p\odot \pi_{s_i} < 0 \;\forall i$]{
        \includegraphics[width=0.3\textwidth]{\figpath plucker_product_a.pdf}
    }
    \subfloat[$\pi_p\odot \pi_{s_i} = 0 \, \exists i$ \newline special]{
        \includegraphics[width=0.3\textwidth]{\figpath plucker_product_b.pdf}
    }
    \subfloat[$\pi_p\odot \pi_{s_i} > 0 \;\forall i$]{
        \includegraphics[width=0.3\textwidth]{\figpath plucker_product_c.pdf}
    }
    \caption{Different relative positions of a line $p$ and a triangle with sides $s_i$, $i=0,1,2$. 
            Signs of the permuted inner products depend on orientation of lines.          
            Dashed line symbolizes that the line is in the back, the lines intersect in the middle case.
            We see that in cases a and c the products have the same sign.
    }
    \label{fig:plucker_products}
\end{figure}
